%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{resume} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Joaqu\'in Iglesias Turina} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{+ 34 676 50 72 64}
\moveleft.5\hoffset\centerline{iglesiastj@gmail.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{OBJECTIVE}  

I am passionate about Statistics and Programming. I want a career
that allows me to focus on those interests.

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{COMPUTER \\ SKILLS} 

 R, Stan, Clojure, Python, OCTAVE, elisp, SQL, Emacs, Linux, 
 Google Cloud Platform, Twitter API, MS Office. \\
 \\
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Economist at BBVA Research} \hfill August 2016 - Present \\
Big Data Unit
\begin{itemize}
\item Taught a course for BBVA Research staff covering the basics of SQL and R.
\item \href{
https://www.bbvaresearch.com/en/publicaciones/how-do-the-emerging-markets-central-bank-talk-a-big-data-approach-to-the-cb-of-turkey/
}
  {Conducted Topic Model analysis on Central Bank Communications}. 
\item Developed an R interface for Google's Natural Language API.
\item Developed an R framework for comparison of time series models' 
  pseudo-out-of-sample performance.
\end{itemize} 

{\sl Teaching Assistant on Big Data and Natural Language Processing} 
\hfill May 2017 \\
Provided practical exercises on Natural Language Processing for 
the Master on Big Data.

{\sl Intern at BBVA Research} \hfill May - August 2015 \\
Cross Country Emerging Markets Unit
\begin{itemize}
\item Developed an R program to access and manipulating the GDELT database.
\end{itemize} 

{\sl Intern at Endesa} \hfill July - December 2014 \\
Forecasting and Controlling.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Master of Science}, Econometrics \hfill 2015 - 2016 \\
University of Amsterdam
Specialized in Micro and Financial Econometrics.

{\sl Bachelor}, Economics \hfill 2010 - 2015 \\
Universidad Carlos III de Madrid
Honors in Industrial Organization and Economic History
Erasmus Scholarship, Vienna University of Economics and Business 
\hfill 2013
Exchange, Long Beach State University, U.S. \hfill 2012-2013

\section{LANGUAGES}

{\sl Spanish}, Native
\bullet
{\sl English}, Bilingual
\bullet
{\sl German}, Basic

%----------------------------------------------------------------------------------------
%	INTERESTS AND ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{INTERESTS AND \\ ACTIVITIES} 
\sl{I believe in continuous education}, \sl{Thus I have attended several MOOCS, including:
Introduction to Complex Analysis}, 
\sl{Algorithms: Design and Analysis I}, 
\sl{Coding the Matrix: Linear Algebra through Computer Science Application}, 
\sl{R Programming}.

Since 2010 until 2015 I played bass professionally in different weddings, events, the National Spanish Concert Hall and the Local and National TV station.
%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
