%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Joaqu\'in}{Iglesias}{
\href{mailto:iglesiastj@gmail.com}{iglesiastj@gmail.com} | 676.507.264
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Amsterdam}
\descript{Msc Econometrics}
\location{2015 - 2016}
Specialized in Micro and Financial Econometrics
\sectionsep

\subsection{Universidad Carlos III \\ de Madrid}
\descript{BS Economics}
\location{2010 - 2015}
Specialized in Game Theory \\ and Econometrics \\
Honors in Industrial Organization and Economic History \\
%% Erasmus Scholarship, Vienna University \\ of Economics and Business \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}

Clojure \textbullet{} Scala \textbullet{} Fennel \textbullet{} Java \\ 
Python \textbullet{} R \textbullet{} Stan \textbullet{} Elisp \textbullet{} \LaTeX\ \\

\sectionsep

\subsection{Computers and \\  Technology}

Postgres \textbullet{} Spark \textbullet{} Databricks \\
Docker \textbullet{} Azure  \textbullet{} Google Cloud  \\
Emacs \textbullet{} Linux \textbullet{} Git \textbullet{} Vault \\

\sectionsep

\subsection{LANGUAGES}

English: Bilingual \textbullet{} Spanish: Native \textbullet{} 
German: Basic \textbullet{} \\
Latin \& Sanskrit: Reading ability \\
\sectionsep

\section{SOFT SKILLS} 
I am radically curious, and selfishly interested in other people's opinions.
While shy and introverted, I seem to have a good people skills.\\

\sectionsep
I believe in continuous education. Thus I have attended several MOOCS, including:
Functional Programming Principles in Scala, and more.\\

\sectionsep
From 2010 to 2015 I played bass professionally in weddings, events, the National Spanish Concert Hall and Local and National TV stations. \\
\sectionsep

\sectionsep
Did you read right? How many people do you know with Sanskrit and Latin reading ability?
That alone should grant me an interview.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OBJECTIVE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Objective}
%% I've managed tasks raging from building backend services and statistical models 
%% to geopolitical analysis and managing clients and customer. I am a strong generalist.

%% I am particularly interested in functional programmin gand bayesian methods.
%% I like and use FOSS. Working on FOSS projects seems like a worth endeavour.
I am a programmer and statistician with experience in Functional Programming, Big Data, Time Series and Bayesian Methods.
I've got significan experience working with Scala, Clojure, R and Python.

I am looking for a position that will allow me to solve complex problems using my skills in an agile and 
intellectually stimulating environment. I want to keep learning on the job, and I belive one of the best ways
to do so is by team work.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Minsait}
\descript{| Senior Consultant. Data Engineer}
\location{ November 2022 - Present | Madrid, Spain}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Lead a team improving code quality and test coverage on a Java Spring app. 
\item Maintainership of a Scala, Spark and Azure product for quality control on data load.
\item Handled interaction with clients.
\end{tightemize}
\sectionsep

\runsubsection{Entrepreneur}
\descript{| Lone Wolf Programmer }
\location{ July 2021 - Novembre 2022 | Madrid, Spain}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Building an app on top of Postgres, Vault, Clojure and Luminus.
\end{tightemize}
\sectionsep

\runsubsection{Gloval Analytics}
\descript{| Senior Data Scientist }
\location{June 2019 – July 2021 | Madrid, Spain}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Automatic Valuation Model. Machine Learning based model for real state appraisal.
\item Supported the data engineering, architecture and back end departments.
\end{tightemize}
\sectionsep

\runsubsection{KPMG D\&A, Advanced Analytics}
\descript{| Senior Data Scientist }
\location{June 2018 – June 2019 | Madrid, Spain}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Python models for churn, cross sell, time series forecasting and price optimization.
%% \item Time series model to forecast sales. Food sector.
%% \item Price optimizer for gas stations. The product provided an engine for dynamic price setting in gas stations,
%% using a time series model of sales and competitors prizing strategy.
%% \item Chatbot to help clients repay debts. Banking sector.
\end{tightemize}
\sectionsep

\runsubsection{BBVA Research}
\descript{| Economist }
\location{August 2016 – June 2018 | Madrid, Spain}
\begin{tightemize}
\item \href{
https://www.bbvaresearch.com/en/publicaciones/how-do-the-emerging-markets-central-bank-talk-a-big-data-approach-to-the-cb-of-turkey/
}
  {Conducted Topic Model analysis on Central Bank Communications}. 
\item R tools for Google Cloud Interaction and out-of-sample model performance. 
%% \item Taught a course for BBVA Research staff covering the basics of SQL and R.
\end{tightemize}
\sectionsep

%% \runsubsection{.aftermath Research}
%% \descript{| Data Scientist }
%% \location{August 2016 – March 2018 | Madrid, Spain}
%% \begin{tightemize}
%% \item Time series modelling of housing prices. The project included a web front built using shinyR. Banking Sector
%% \item Panel data modelling of insurance premia across the world. Insurance Sector
%% \end{tightemize}
%% \sectionsep

\runsubsection{Deusto Business School}
\descript{| Big Data Teaching Assistant }
\location{ May 2017 | Madrid, Spain}
Provided practical exercises on Natural Language Processing.
\sectionsep

\runsubsection{BBVA Research}
\descript{| Intern }
\location{May - August 2015 | Madrid, Spain}
%% \begin{tightemize}
%%  %% \item Developed an R program to access and manipulating the GDELT database through Google Cloud.
%% \end{tightemize} 

%% \runsubsection{Endesa, Forecasting and Controlling}
%% \descript{| Intern }
%% \location{July - December 2014 | Madrid, Spain}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OPEN SOURCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{OPEN SOURCE}
\runsubsection{Azufre}
\descript{| A Fennel wrapper over the Azure cli }
\href{https://git.sr.ht/~jiglesias/azufre}{Created a tool} 
for comfortable and repl driven Azure management.
\sectionsep

\runsubsection{ZIO}
\descript{| A Scala library for functional programming }
\href{https://github.com/zio/zio/pull/7600}{Updated mocking documentation} 
from version 1.0 to 2.0.
\sectionsep

\runsubsection{min-love2d-fennel}
\descript{| Minimal Fennel Love2D Setup }
\href{https://gitlab.com/alexjgriffith/min-love2d-fennel/-/issues/10}{Added a feature} 
to use an unreleased version of LOVE2D. What could possible go wrong?
\sectionsep

\end{minipage} 
\end{document}
