%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Joaqu\'in}{Iglesias}{
\href{mailto:iglesiastj@gmail.com}{iglesiastj@gmail.com} | 676.507.264
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Amsterdam}
\descript{Msc Econometrics}
\location{2015 - 2016}
Specialized in Micro and Financial Econometrics
\sectionsep

\subsection{Universidad Carlos III \\ de Madrid}
\descript{BS Economics}
\location{2010 - 2015}
Specialized in Game Theory \\ and Econometrics \\
Honors in Industrial Organization and Economic History \\
%% Erasmus Scholarship, Vienna University \\ of Economics and Business \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}

R \textbullet{} Python \textbullet{} Clojure \textbullet{} \LaTeX\ \\ 
Stan \textbullet{} Elisp \textbullet{} Octave \textbullet{} JavaScript \\

\sectionsep

\subsection{Computers and \\  Technology}

Spark \textbullet{} Databricks \textbullet{} Git \textbullet{} Jira \\
Azure  \textbullet{} Google Cloud \textbullet{} Emacs \textbullet{} Linux \\

\sectionsep

\subsection{LANGUAGES}

English: Bilingual \textbullet{} Spanish: Native \textbullet{} German: Basic \\

\sectionsep

\section{INTERESTS AND \\ ACTIVITIES} 
I believe in continuous education. Thus I have attended several MOOCS, including:
Functional Programming Principles in Scala,\\
Algorithms: Design and Analysis,\\
Coding the Matrix: Linear Algebra through Computer Science Application \\
\sectionsep
From 2010 to 2015 I played bass professionally in weddings, events, the National Spanish Concert Hall and Local and National TV stations.
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OBJECTIVE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Objective}
I am a statistician and programmer with experience in Time Series, Bayesian Methods and Machine Learning and working
mostly in R and Python.
I am looking for a position that will allow me to solve complex problems using my skills in a dynamic, agile and 
intellectually stimulating environment. I want to keep learning on the job, and I belive one of the best ways
to do so is by team work.  
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}


\runsubsection{Gloval Analytics}
\descript{| Senior Data Scientist }
\location{June 2019 – Present | Madrid, Spain}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Automatic Valuation Model. Machine Learning based model for real state appraisal.
\item I have also been involved with the data engineering and architecture departments, 
as well as taken part in web development tasks.
\end{tightemize}
\sectionsep


\runsubsection{KPMG D\&A, Advanced Analytics}
\descript{| Senior Data Scientist }
\location{June 2018 – June 2019 | Madrid, Spain}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Marketing next best action system in Spark. The project included both churn and cross-sell Machine Learning
models and a recommender system. All pieces were integrated to provide the marketing department the next
best action to take on a client.
Insurance sector.
\item Time series model to forecast sales. Food sector.
%% \item Price optimizer for gas stations. The product provided an engine for dynamic price setting in gas stations,
%% using a time series model of sales and competitors prizing strategy.
%% \item Chatbot to help clients repay debts. Banking sector.
\end{tightemize}
\sectionsep

\runsubsection{BBVA Research}
\descript{| Economist }
\location{August 2016 – June 2018 | Madrid, Spain}
\begin{tightemize}
\item \href{
https://www.bbvaresearch.com/en/publicaciones/how-do-the-emerging-markets-central-bank-talk-a-big-data-approach-to-the-cb-of-turkey/
}
  {Conducted Topic Model analysis on Central Bank Communications}. 
\item Developed an R interface for Google's Natural Language API.
\item Developed an R framework for comparison of time series models' 
  pseudo-out-of-sample performance.
%% \item Taught a course for BBVA Research staff covering the basics of SQL and R.
\end{tightemize}
\sectionsep

\runsubsection{.aftermath Research}
\descript{| Data Scientist }
\location{August 2016 – March 2018 | Madrid, Spain}
\begin{tightemize}
\item Time series modelling of housing prices. The project included a web front built using shinyR. Banking Sector
\item Panel data modelling of insurance premia across the world. Insurance Sector
\end{tightemize}
\sectionsep

\runsubsection{Deusto Business School}
\descript{| Teaching Assistant}
\location{ May 2017 | Madrid, Spain}
Provided practical exercises on Natural Language Processing for 
the Master on Big Data.
\sectionsep

\runsubsection{BBVA Research}
\descript{| Intern }
\location{May - August 2015 | Madrid, Spain}
\begin{tightemize}
\item Developed an R program to access and manipulating the GDELT database through Google Cloud.
\end{tightemize} 

%% \runsubsection{Endesa, Forecasting and Controlling}
%% \descript{| Intern }
%% \location{July - December 2014 | Madrid, Spain}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OPEN SOURCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{OPEN SOURCE}
\runsubsection{Incanter}
\descript{| Clojure-based, R-like statistical computing and graphics environment for the JVM}
\location{}
\href{https://github.com/incanter/incanter/pull/396/files}{Contributed code} for Weighted Least Squares,
Iteratively Reweighted Least Squares Algorithm and Robust Linear Regression. Currently working on a GLM implementation.
\sectionsep

\end{minipage} 
\end{document}
